---
title: "Regex"
output: html_document
date: "`r Sys.Date()`"
---
Uploading required package:
```{r}
library(dplyr)
MData <- read.csv("measurements.csv")
```

Inspecting the dataframe:
NOTE: Because the CSV was created using the "dataGenerato" code chunk, this dataframe doesn't include the Volume column generated from "volumeEstimato." However, it does not matter for this assignment so leaving it as is.
```{r}
tail(MData)
```
```{r}
head(MData)
```
```{r}
summary(MData)
```
```{r}
str(MData)
```
```{r}
dim(MData)
```

Using regular expressions and dplyr to change genus name:
NOTE: In assignment 1, my column was titled "species" rather than "Organism," so that's what we're working with here
```{r}
MData <- MData %>%
  mutate(Sp = gsub("(\\w)\\w+(.*)","\\1\\.\\2", measurements$species)) %>% #regular expression to change genus name to first letter
  select(Sp, everything()) %>% #Moving Sp column to beginning of dataframe
  select(-c(species)) #Dropping the species column 
head(MData)
```
```{r}
tail(MData)
```

```{r}
write.csv(MData, "MeasShort.csv", row.names=FALSE)
```
